Reviewer comments from PeerJ

### 2015-03-23 PeerJResponse.tex
Edits
LV edits to page & line numbers

\lev{Hi guys, I'm having trouble getting the figures to renumber in order and haven't been able to figure out what's going on, if either of you knows how to fix or has a suggestion.}

\mbh{I fixed this}

@@

\res{Data were previously phased using the program fastPHASE (\citet{Pyhajarvi2013, Scheet2006}). We have added clarifying statements to the text of this section, pages 5, lines 104-105. \mbh{please go through and recheck these line numbers just prior to submitting revisions} Figure 4 is showing maize population assignment for adjacent 5 kb windows. The STRUCTURE analysis was performed for the entirety of chromosome 1; however, the figure only shows a zoomed in portion to highlight the section of chromosome 1 that contains the \emph{tb1} region. The results in Table 4 reflect the entire chromosome.}

@@

\res{We have edited our discussion to include a brief mention of the work by \citet{LukensDoebley1999}, page 12, lines 344-346: ``We have found no significant effect of the \emph{Hopscotch} insertion on tillering index or tiller number, a result that is discordant with its clear phenotypic effects in maize. It is possible that the planting density of our seedlings (plants spaced 12 inches apart) was too high, leading to an overall decrease in tillering as previously seen in \citet{LukensDoebley1999}.  This factor may have limited our capacity to observe variation in tillering index."}

\lev{My guess is that later on our plants were crowded, but early on in the measurements they should not have been shading each other, and tillering then would not have been affected in the early measurements. What do you guys think?}

\mbh{I read the Lukens and Doebley paper and I think what you had previously was backwards...higher density = less tillering, not more.  If we saw less overall tillering due to high density, this could have compromised our ability to detect significant differences between genotypes.}

@@

\res{We have editied the text to provide further clarification, page 8, lines 211-213: ``To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region and any evidence of selection on this locus, we sequenced two small ($<$1kb) regions upstream of the \emph{tb1} ORF in four populations from the Jalisco region."}

>>>>

@@

\res{Data were previously phased using the program fastPHASE (\citet{Pyhajarvi2013, Scheet2006}). We have added clarifying statements to the text of this section, pages 5, lines 105-108. Figure 4 is showing maize population assignment for adjacent 5 kb windows. The STRUCTURE analysis was performed for the entirety of chromosome 1; however, the figure only shows a zoomed in portion to highlight the section of chromosome 1 that contains the \emph{tb1} region. The results in Table 4 reflect the entire chromosome.}

@@

\res{We have edited our discussion to include a brief mention of the work by \citet{LukensDoebley1999}, page 13, lines 358-360: ``We have found no significant effect of the \emph{Hopscotch} insertion on tillering index or tiller number, a result that is discordant with its clear phenotypic effects in maize. It is possible that the planting density of our seedlings (plants spaced 12 inches apart) was too high, leading to an overall decrease in tillering as previously seen in \citet{LukensDoebley1999}.  This factor may have limited our capacity to observe variation in tillering index."}

@@

\res{We have editied the text to provide further clarification, page 8, lines 222-225: ``To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region and any evidence of selection on this locus, we sequenced two small ($<$1kb) regions upstream of the \emph{tb1} ORF in four populations from the Jalisco region."}
